%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh Gadgil
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

% Command for printing skill progress bars
\newcommand\skills{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Linux},
        \textbf{Mobile}\\\textbf{Devices},
        \textbf{Android}\\\textbf{Dev},
        \textbf{SDK}\\\textbf{Design},
        \textbf{Embedded}\\\textbf{System},
        \textbf{Continuous}\\\textbf{Integration},
        \textbf{Scrum},
        \textbf{GIS/Maps}
    }
}

\interests{{DevOps/5},{Location Based Services/6},{Network Streaming/6}}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}



\cvname{Peng Liu} % Your name
\cvjobtitle{ Software Engineer, \\ Mobile Developer} % Job title/career

\cvlinkedin{https://linkedin.com/in/peng-liu}
\cvgithub{https://github.com/pengdev}
\cvnumberphone{+358 41 7086 582} % Phone number
\cvsite{http://www.liupeng.eu/} % Personal website
\cvmail{liupengking1@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem
    	{2011 - 2015}
        {MSc., Communications Engineering}
        {\href{http://www.aalto.fi/en/}{Aalto University}}
        {Helsinki, Finland}
        {GPA: 4.04/5, Completed with Distinction}
	\twentyitem
    	{2007 - 2011}
        {BEng.,  Electronic and Information Engineering}
        {\href{http://www.xtu.edu.cn/english/}{Xiangtan University}}
        {Xiangtan, Hunan, China}
        {GPA: 3.51/4, Ranked 1/76}
	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}


\section{Research}
\begin{twenty}
	\twentyitem
    	{June 2012 - \\Dec 2012}
        {Research Assistant}
        {\href{https://www.helsinki.fi/en}{University of Helsinki}}
        {}
        {
        {\begin{itemize}
        \item Participated in the Internet of Things project, set up	 frameworks on Linux to evaluate different protocols over Internet of Things.
        \item Participated in the WiBrA project,	 updated	 the	 implementation of routing protocol in Linux kernel and	 user-space, tested in real operator networks on the mobile platform.
    \end{itemize}}
        }
\end{twenty}

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
    \twentyitem
    	{Aug 2019 - \\Present}
        {Senior Android Engineer, Maps SDK}
        {\href{http://www.mapbox.com/}{Mapbox Inc.}}
        {}
        {
        {\begin{itemize}
        \item Working on the Mapbox's Maps SDK for Android.
    \end{itemize}}
        }
	\twentyitem
    	{Jan 2013 - \\ Aug 2019}
        {Software Engineer \& Mobile Developer}
        {\href{http://www.tuxera.com/}{Tuxera Inc.}}
        {}
        {
        {\begin{itemize}
        \item \textit{Product Demo Projects} \\Built product demos for Tuxera's filesystem products, technologies used include Python, NodeJS, ReactJS and Docker.
        \item \textit{AllConnect Project} \\Worked in a agile team of 8, finished the design and implementation of DLNA protocol stack for the AllConnect SDK on both Android and iOS platforms, developed and released the AllConnect App in Google Play Store and iOS store. Now the app has accumulated over 10 million downloads and was selected as the 2017 CES Innovation Award Honoree in software and mobile apps section.
        \item \textit{DLNA project} \\Worked independently on debugging and improving the open source DLNA media server on Linux, ported it to both ASUS-WRT and Android platform. The improved binary passed the DLNA media server certification test suite and UPnP test suite.
        \item \textit{Master Thesis} \\Finished my master thesis based on the AllConnect project, implemented and integrated cross-platform multimedia streaming technologies, such as DLNA, Chromecast, Fire TV and AirPlay, in the commercial mobile application product.
    \end{itemize}}
        }
        
    \twentyitem
   		{Sep 2012 - \\ May 2013}
        {Project Developer}
        {\href{http://www.aalto.fi/en/}{Aalto University}}
        {}
        {
        {\begin{itemize}
        \item Worked in a team of 9 people with various background. The indoor positioning project was funded and supported by Ericsson and Aalto University. The indoor positioning prototype was built using WiFi fingerprint technology and the final products are an Android application, an Android calibration tool and a positioning engine with room-level accuracy.
    \end{itemize}}
        }
        
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

\end{document} 
